### 2017-01-10 README.Rmd
updated README

In this example, we fit a random forest to the Boston housing data. (See `?boston` for a brief explanation of the data.) Note, for any of the following examples, you can see a progress bar by simply specifying `progress = "text"` in the call to `partial`. You may also reduce the computation time via the `grid.resolution` option in the call to `partial`.
```{r, message = FALSE, warning=FALSE, fig.width=12, fig.height=4}
# Load required packages
library(pdp)  # for constructing PDPs
library(randomForest)  # for random forest algorithm

@@

# Partial dependence of lstat and rm on cmedv
grid.arrange(
  partial(boston.rf, pred.var = "lstat", plot = TRUE, rug = TRUE),
  partial(boston.rf, pred.var = "rm", plot = TRUE, rug = TRUE),
  partial(boston.rf, pred.var = c("lstat", "rm"), plot = TRUE, chull = TRUE),
  ncol = 3
)

```

@@

Finally, we demonstrate the construction of PDPs from models fit using the `caret` package; `caret` is an extremetly useful package for classification and regression training that, essentially, has one function (`train`) for fitting all kinds of predictive models in R (e.g., `glmnet`, `svm`, `xgboost`, etc.).

@@

# Set up for 5-fold cross-validation
ctrl <- trainControl(method = "cv", number = 5)

# Grid of tuning parameter values
xgb.grid <- expand.grid(
  nrounds = c(1000, 2000),
  max_depth = 2:4,
  eta = c(0.001, 0.01, 0.1),
  gamma = 0, 
  colsample_bytree = 1,
  min_child_weight = 1,
  subsample = c(0.5, 0.75, 1)
)

# Tune am XGBoost model to the Pima Indians diabetes data. This may take a few 
# minutes!
set.seed(103)  # for reproducibility
pima.xgb <- train(diabetes ~ ., data = pima, method = "xgbTree",
                  prob.model = TRUE, na.action = na.omit, trControl = ctrl,
                  tuneGrid = xgb.grid)

# Partial dependence of glucose and age on diabetes test result (neg/pos)
grid.arrange(
  partial(pima.xgb, pred.var = "glucose", plot = TRUE, rug = TRUE),
  partial(pima.xgb, pred.var = "age", plot = TRUE, rug = TRUE),
  partial(pima.xgb, pred.var = "mass", plot = TRUE, rug = TRUE),
  ncol = 3 
)
```

>>>>

In this example, we fit a random forest to the Boston housing data. (See `?boston` for a brief explanation of the data.) Note, for any of the following examples, you can see a progress bar by simply specifying `progress = "text"` in the call to `partial`. You may also reduce the computation time via the `grid.resolution` option in the call to `partial`.
```{r, message = FALSE, warning=FALSE, fig.width=12, fig.height=4}
# Load required packages
library(ggmap)  # for plotting maps with ggplot2
library(pdp)  # for constructing PDPs
library(randomForest)  # for random forest algorithm

@@

# Partial dependence of cmedv on lstat and rm
grid.arrange(
  partial(boston.rf, pred.var = "lstat", plot = TRUE, rug = TRUE),
  partial(boston.rf, pred.var = "rm", plot = TRUE, rug = TRUE),
  partial(boston.rf, pred.var = c("lstat", "rm"), plot = TRUE, chull = TRUE),
  ncol = 3
)

# Look at partial dependence of median home value on location
pd.loc <- partial(boston.rf, pred.var = c("lon", "lat"), chull = TRUE)

# Overlay predictions on a map of Boston
ll <- c(range(boston$lon), range(boston$lat))
map <- get_map(location = ll[c(1, 3, 2, 4)], zoom = 11, maptype = "toner-lite")
ggmap(map) +
  geom_point(aes(x = lon, y = lat), data = boston, alpha = 0.2) +
  geom_tile(aes(x = lon, y = lat, fill = yhat),
            data = pd.loc, alpha = 0.3) +
  scale_fill_distiller(palette = "Spectral", name = "Median\nvalue") +
  coord_fixed(ratio = 1) +
  labs(x = "Longitude", y = "Latitude")
```

@@

Finally, we demonstrate the construction of PDPs from models fit using the `caret` package; `caret` is an extremetly useful package for training all sorts of predictive models in R (e.g., `glmnet`, `svm`, `xgboost`, etc.).

@@

# Tune an XGBoost model to the Pima Indians diabetes data. This may take a few 
# minutes!
set.seed(103)  # for reproducibility
pima.xgb <- train(diabetes ~ ., data = pima, 
                  method = "xgbTree",
                  na.action = na.omit,
                  trControl = trainControl(method = "cv", number = 5),
                  tuneLength = 5)

# Partial dependence of glucose and age on diabetes test result (neg/pos)
grid.arrange(
  partial(pima.xgb, pred.var = "glucose", plot = TRUE, 
          rug = TRUE, smooth = TRUE),
  partial(pima.xgb, pred.var = "age", plot = TRUE, 
          rug = TRUE, smooth = TRUE),
  partial(pima.xgb, pred.var = "mass", plot = TRUE, 
          rug = TRUE, smooth = TRUE),
  ncol = 3 
)
```
